Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-01 article_springer/article_springer.Rmd
Clean Up Bibtex File, delte DOIs
2 small Typos

## Algorithm for the inference on exceedance times

@@

: After removing the "noise observations" below the smallest threshold 
  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is iid 
  An indication if this is true is given by an auto-correlation plot. Since we are expecting the inter-exceedance times to be Mittag-Leffler distributed and hence to have infinite mean but finite log-moments, we first take the logarithms of the times.

@@

The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package. Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education andResearch (BMBF)

>>>>

## Algorithm for the inference on inter-exceedance times

@@

: After removing the "noise observations" below the smallest threshold 
  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is iid. 
  An indication if this is true is given by an auto-correlation plot. Since we are expecting the inter-exceedance times to be Mittag-Leffler distributed and hence to have infinite mean but finite log-moments, we first take the logarithms of the times.

@@

The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package. Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education and Research (BMBF).
